### 2011-10-31 doc/theses/vitasek/chapter-2-research.tex
Thesis: in progress.

Fajt in \cite{fajt} introduces several algorithms to find XML keys (see \cite{keX}) in existing XML documents. Simple keys found this way can be translated to an equivalent ID attribute definition. The process is described in \cite[Ch.\ 9, s.\ 3]{vlist2002xml}. This opens a new line of research: finding XML keys using an algorithm modified to look only for \textit{useful} keys and then converting them to ID attributes.\\

>>>>

Fajt in \cite{fajt} introduces several algorithms to find XML keys (see \cite{keX}) in existing XML documents. Simple keys found this way can be translated to an equivalent \texttt{ID} attribute definition. The process is described in \cite[Ch.\ 9, s.\ 3]{vlist2002xml}. This opens a new line of research: finding XML keys using an algorithm modified to look only for \textit{useful} keys and then converting them to \texttt{ID} attributes.\\

### 2011-10-31 doc/theses/vitasek/chapter-4-1-experiments-setup.tex
Thesis: in progress.

\subsection{Realistic data}
\label{section-realistic-data}

@@

\subsection{Realistic data with artificial attributes}
\label{section-realistic-converted}

@@

This approach is useful, because as mentioned in Chapter \ref{chapter-research}, ID attributes are a special case of XML keys. We can use this approach to find XML keys: convert some ``suspicious'' data into attributes, find the optimal ID set and then create XML key based on this ID set.

@@

In case of \dataset{MSH} we created 2 attributes, of which only one constituted a candidate AM. This is then the case similar to \dataset{XMA-*} sets: quite large data, yet only one trivial ID attribute to be found.

@@

\subsection{Artificial data}

@@

\begin{algorithm}
\caption{Random XML data creation}
\label{listing-random-data}
\begin{algorithmic}
\REQUIRE $v$ requested number of vertices
\REQUIRE $e$ requested number of edges
\ENSURE XML file content
\PRINT \texttt{<graph>}
\FOR{$i = 1 \to |V|$}
	\STATE $R \gets RANDOM$
	\PRINT \texttt{<vertex\textit{i} attr="\textit{R}">}
\ENDFOR
\FOR{$i = 1 \to |E|$}
	\STATE $v1 \gets RANDOM(|V|)$
	\STATE $v2 \gets RANDOM(|V|)$
	\PRINT \texttt{<vertex\textit{v1} attr="\textit{i}"> <vertex\textit{v2} attr="\textit{i}">}
\ENDFOR
\PRINT \texttt{</graph>}
\RETURN
\end{algorithmic}
\end{algorithm}

@@

There is a tuple for every attribute node with a value found in the initial grammar. Note that the information about the context in which the element was originally found is lost - but this is not a problem with regard to the definition of XML ID attributes. Furthermore, tuples in flat representation do not need to be unique.\\

>>>>

\subsection{Realistic Data}
\label{section-realistic-data}

@@

\subsection{Realistic Data With Artificial Attributes}
\label{section-realistic-converted}

@@

This approach is useful, because as mentioned in Chapter \ref{chapter-research}, \texttt{ID} attributes are a special case of XML keys. We can use this approach to find XML keys: convert some ``suspicious'' data into attributes, find the optimal ID set and then create XML key based on this ID set.

@@

In case of \dataset{MSH} we created 2 attributes, of which only one constituted a candidate AM. This is then the case similar to \dataset{XMA-*} sets: quite large data, yet only one trivial \texttt{ID} attribute to be found.

@@

\subsection{Artificial Data}

@@

\begin{algorithm}
\caption{Random XML Data Creation}
\label{listing-random-data}
\begin{algorithmic}
\REQUIRE $v$ requested number of vertices
\REQUIRE $e$ requested number of edges
\ENSURE XML file content
\PRINT \texttt{<graph>}
\FOR{$i = 1 \to |V|$}
	\STATE $R \gets RANDOM$
	\PRINT \texttt{<vertex\textit{i} attr="\textit{R}">}
\ENDFOR
\FOR{$i = 1 \to |E|$}
	\STATE $v1 \gets RANDOM(|V|)$
	\STATE $v2 \gets RANDOM(|V|)$
	\PRINT \texttt{<vertex\textit{v1} attr="\textit{i}"> <vertex\textit{v2} attr="\textit{i}">}
\ENDFOR
\PRINT \texttt{</graph>}
\RETURN
\end{algorithmic}
\end{algorithm}

@@

There is a tuple for every attribute node with a value found in the initial grammar. Note that the information about the context in which the element was originally found is lost - but this is not a problem with regard to the definition of XML \texttt{ID} attributes. Furthermore, tuples in flat representation do not need to be unique.\\

### 2011-10-31 doc/theses/vitasek/chapter-6-conclusion.tex
Thesis: in progress.

From all the integrity constraints in XML we chose the ID / IDREF / IDREFS attributes and decided to improve upon the search for them. We discussed the approach from \cite{fidax} and the equivalence of ID set search and maximum weighted independent set. Based on this article we introduced the MIP approach and demonstrated how to find the optimal ID set using external GLPK solver in the environment of jInfer framework.\\

@@

To the best of our knowledge, at the time of writing this work is our approach to finding ID attributes the best one known.

>>>>

From all the integrity constraints in XML we chose the \texttt{ID}/\.\texttt{IDREF}/\.\texttt{IDREFS} attributes and decided to improve upon the search for them. We discussed the approach from \cite{fidax} and the equivalence of ID set search and maximum weighted independent set. Based on this article we introduced the MIP approach and demonstrated how to find the optimal ID set using external GLPK solver in the environment of jInfer framework.\\

@@

To the best of our knowledge, at the time of writing this work is our approach to finding \texttt{ID} attributes the best one known.
